Order statistics and numerical optimization: the case of a single observation

### 2021-02-02 inst/cook.Rmd
bugfix

```{r,beforetraining}
H <- hyper2(pnames=c(paste("p",1:5,sep="")))  # 'S' the strength of training
# observations before training:
Hbefore <- H +
  race(c("p5","p2","p3","p4","p1")) + #  5 is the best, 4 the worst.
  race(c("p5","p3","p2","p4","p1")) + #  5 is the best, 1 the worst.
  race(c("p4","p5","p3","p2","p1")) + #  4 is the best, 1 the worst.
  race(c("p5","p3","p4","p1","p2")) + #  5 is the best, 2 the worst.
  race(c("p2","p5","p3","p1","p4"))   #  2 is the best, 4 the worst.
Hbefore
```

@@

```{r,addbeforeandafter}
pnames(Hbefore) <- c(pnames(Hbefore),"S")
maxp(Hbefore+Hafter)
```

>>>>

```{r,beforetraining}
# observations before training:
Hbefore <- 
  race(c("p5","p2","p3","p4","p1")) + #  5 is the best, 4 the worst.
  race(c("p5","p3","p2","p4","p1")) + #  5 is the best, 1 the worst.
  race(c("p4","p5","p3","p2","p1")) + #  4 is the best, 1 the worst.
  race(c("p5","p3","p4","p1","p2")) + #  5 is the best, 2 the worst.
  race(c("p2","p5","p3","p1","p4"))   #  2 is the best, 4 the worst.
Hbefore
```

@@

```{r,addbeforeandafter}
maxp(Hbefore+Hafter)
```

### 2021-02-02 inst/order.Rmd
fixes #39
bugfix

```{r defineH}
library("hyper2")
H <- order_likelihood(rbind(1:10))
H
```
And then maximizing it is carried out using the `maxp()` function:

@@

Comparing the numerically determined maximum likelihood estimate with
the exact MLE of $(1,0,\ldots,0)$ shows that the numerics have not
done a particularly good job in identifying the evaluate, presumably
as a result of the difficulty of honouring the constraints.  However,
if we give the system a hand by starting at a point closer to the
evaluate we can do much better:

>>>>

```{r defineH}
library("hyper2")
H <- race(letters[1:10])
H
```
And then maximizing it is carried out using the `maxp()` function:

@@

Comparing the numerically determined maximum likelihood estimate with
the exact MLE of $(1,0,\ldots,0)$ shows that the numerics have not
done a particularly good job in identifying the evaluate, presumably
as a result of the difficulty of honouring the constraints.  However,
if we give the system a hand by starting at a point closer to the
evaluate we can do slightly better:
